---
title: "Supplementary Figures & Presentation of Discovery dataset"
author: "Diana Proctor"
date: "December 16, 2017"
output:
  html_document: default
  pdf_document: default
---

Nature Communications Supplementary Data File 2 - 

This is the SECOND script used to generate the main figures for the the manuscript by Proctor et al. titled "A spatial gradient of bacterial diversity in the human oral cavity shaped by salivary flow" 


<WORK> This script and associated data are provided via (c) by Diana M Proctor, Julia A. Fukuyama, Susan P. Holmes, David A. Relman. These data and the associated script are licensed under the Creative Commons Attribution-ShareAlike 4.0 International License (CC-BY-CA).

Given attribution, you are free to:
1) Share, copy and redistribute the material in any medium or format
2) Adapt, remix, transform, and build upon the material for any purpose, even commercially.

To see the full license associated with attribution of this work, see the CC-By-CA license,  see <http://creativecommons.org/licenses/by-sa/4.0/>.


### Import the data from the "Main Figures" script
Run the "Main Figures" script first. Then run this one. Most of the supplemental figures are in two accompanying files, one for beta diversity, and the one to generate the other supplemental figures in the manuscript. The local name of this file on my desktop is: NatureComm_SupplementalFigures.Rmd.


```{r}
library("phyloseq");library("ggplot2");library(gridExtra);library("stringr");library("reshape2");library("genefilter"); library(knitr);library(DESeq2)
setwd("~/Desktop/Proctor_NatureComm/")
load("~/Desktop/Proctor_NatureComm/Proctor_MainFigures_v28.0.Rdata")
```


###Map of the samples by site and subject
```{r, fig.height=8, fig.width=12}
df <- data.frame(sample_data(supra))
teeth <- 3:30
days <- 1:30
df$Tooth <- factor(df$Tooth_Number, as.character(teeth))
df$Day <- factor(df$Day, as.character(days))

p=ggplot(df, aes(Tooth, Day, color=Tooth_Class, shape=Tooth_Aspect)) + geom_point() + facet_wrap(~Subject) + theme_bw() + theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1))+ scale_x_discrete(breaks = seq(from=0, to=35, by=5), labels=seq(from=0, to=35, by=5))  + scale_y_discrete(breaks = seq(from=0, to=35, by=5), labels=seq(from=0, to=35, by=5)) 

p
```


#### Supplemental Figure 1:  PCoA alternative axes
```{r}
#hellinger transform the data
otus = data.frame(otu_table(index25))     
library(vegan)
otus.h = decostand(otus, "hellinger")  

#Do PCOA
#nmds on bray curtis distance of hellinger transformation
h.euc = vegdist(otus.h, "bray")
h.nmds = cmdscale(h.euc, eig=TRUE, k=10)
h.map = data.frame(sample_data(index25), scores(h.nmds))
h.map$method = "Hellinger"
h.eig = 100*(h.nmds$eig/sum(h.nmds$eig))
head(h.eig)

#make a screeplot
evals <- h.nmds$eig
foo = data.frame(h.eig, as.numeric(1:length(h.eig)))
colnames(foo) = c("percent.variation", "rank")
p=ggplot(foo[1:10,], aes(rank, percent.variation)) + geom_point() + theme_bw()
p

#
varEX = 100*(evals/sum(evals))
head(varEX)
```

##### 1b. Supplementary Figure S1: NMDS - lookat like we may want to look at the first 4 axes
- we see that the only axis that gives rise to a horsehow structure is axis 4; along axis 1 there is segregation of most molar and incisor samples

```{r, fig.height=8, fig.width=12}
nmds.df = data.frame(scores(h.nmds)[,1:4], sample_data(index25))
############Color by tooth class 
#axis 1 vs. 2, 3, 4 - color plots by tooth class
p1 = ggplot(nmds.df, aes(Dim1, Dim2, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point() + theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=8), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1)) +coord_fixed(sqrt(evals[2] / evals[1])) + xlab("Dim 1 (23.5%)")+ ylab("Dim 2 (10.9%)") + ggtitle("a)")


p2 = ggplot(nmds.df, aes(Dim1, Dim3, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point()+ theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=8), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1))+coord_fixed(sqrt(evals[3] / evals[1]))+ xlab("Dim 1 (23.5%)")+ ylab("Dim 3 (9.7%)") + ggtitle("b)")


p3 = ggplot(nmds.df, aes(Dim1, Dim4, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point()+ theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=8), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1))+coord_fixed(sqrt(evals[4] / evals[1])) + xlab("Dim 1 (23.5%)")+ ylab("Dim 4 (8.0%)")+ ggtitle("c)")

#axis 2 vs. 3, 4
p4 = ggplot(nmds.df, aes(Dim2, Dim3, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point()+ theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=8), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1))+coord_fixed(sqrt(evals[2] / evals[3])) + xlab("Dim 2 (10.9%)")+ ylab("Dim 3 (9.7%)")+ ggtitle("d)")

p5 = ggplot(nmds.df, aes(Dim2, Dim4, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point()+ theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=8), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1))+ xlab("Dim 2 (10.9%)")+ ylab("Dim 2 (8%)")+coord_fixed(sqrt(evals[2] / evals[4]))+ ggtitle("e)")

#axis 3 vs. 4
p6 = ggplot(nmds.df, aes(Dim3, Dim4, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point()+ theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=8), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1))+coord_fixed(sqrt(evals[3] / evals[4]))+ xlab("Dim 3 (9.7%)")+ ylab("Dim 4 (8%)")+ ggtitle("f)")

grid.arrange(p1, p2, p3,p4, p5, p6, ncol=3)

#ggsave(grid.arrange(p1, p2, p3, p4, p5, p6, ncol=2), file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS1.pdf",  width = 11, height = 8.5, units ="in",dpi = 300)  
```


#### Supplemental Figure 2: Robust to a variety of transformations
### Set up several otu tables with different transformations
```{r, fig.width=12, fig.height=9}
### Create an index tooth biogeography subset
index <- subset_samples(supra, Protocol=="Home")
sites <- c("Molar", "Incisor_Central")
index_subsites <- subset_samples(index, Tooth_Class %in% sites)
index_subsites
        
#how many samples are in average 2 subjects? Looks like about 25% of samples
mean(table(sample_data(index_subsites)$Subject))

#filter the taxa to include those present in 25% of samples
filtergroup = filterfun(kOverA(k=850, A=1)) #k = number of samples; A = abundance
        index25 = filter_taxa(index_subsites, filtergroup, prune=TRUE) 
        index25 = prune_samples(sample_sums(index25) > 0, index25) 

        #note the following command drops 7 samples (depth between 1-35)
        index25 = prune_samples(sample_sums(index25) > 800, index25) 
        index25

#VST transform the index25 dataset
        
#Stabilize the variance with a transformation
Index25_VST <- index25
#add 1 to OTU counts
otu_table(Index25_VST) <- otu_table(Index25_VST) + 1
#create deseq object
Index25.ds = phyloseq_to_deseq2(Index25_VST, ~Tooth_Class)
#regularlized log transformation
Index25.VST <- varianceStabilizingTransformation(Index25.ds, blind=TRUE, fitType = "local") 
counts_full_VST <- otu_table(as.matrix(assay(Index25.VST)), taxa_are_rows=TRUE)
#exchange otu tables
otu_table(Index25_VST) <- counts_full_VST 

#convert all the data to relative abundance        
indexRA = transform_sample_counts(index25, function(x) x / sum(x))

#####################get the otu tables
library(vegan)
#raw data
otus = data.frame(otu_table(index25))

#vst-transformed data
otus.VST = data.frame(t(otu_table(Index25_VST)))

#Relvative abundance-transformed data
otus.RA = transform_sample_counts(index25, function(x) x / sum(x))
otus.ra = as.matrix(otu_table(otus.RA))

#hellinger transform
otus.h = as.matrix(decostand(otus, "hellinger"))

#chi-square
otus.chi = decostand(otus, "chi.square")

# Orlóci's Chord distance: range 0 .. sqrt(2)
otus.c = vegdist(decostand(otus, "norm"), "euclidean")
```

### plot the standard deviation as a function of the mean after various transformations

```{r}
library(vsn)
#raw data
raw= meanSdPlot(as.matrix(otus), rank=FALSE) 
p1= raw$gg + theme_bw()+ ggtitle("Raw")

#vst data
vst=meanSdPlot(as.matrix(otus.VST), rank=FALSE) 
p2 = vst$gg + theme_bw()+ ggtitle("VST")

#hellinger
hel = meanSdPlot(as.matrix(otus.h), rank=FALSE)
p3 = hel$gg + theme_bw()+ ggtitle("Hellinger")

#chi-squared
chi=meanSdPlot(as.matrix(otus.chi), rank=FALSE)  
p4 = chi$gg + theme_bw()+ ggtitle("Chi-Square")

#chord
chor= meanSdPlot(as.matrix(otus.c), rank=FALSE) 
p5 = chor$gg + theme_bw()+ ggtitle("Chord")

````

### Plot the sd over mean 
```{r, fig.height=8, fig.width=12}
grid.arrange(p1, p2, p3, p4, p5, ncol=3)
```

#### Supplementary figure S2: nmds on euclidean distance following the different transformations
```{r, fig.width=12, fig.height=9}
library(stringr)
sample_data(index25)$Tooth_Class = str_replace_all(sample_data(index25)$Tooth_Class, "Incisor_Central", "Incisor")
#nmds on euclidean distance of hellinger transformation
h.euc = vegdist(otus.h, "euclidean")
h.nmds = cmdscale(h.euc, eig=TRUE, k=10)
h.map = data.frame(sample_data(index25), scores(h.nmds))
h.map$method = "Hellinger"
h.eig = 100*(h.nmds$eig/sum(h.nmds$eig))
h.eval = h.nmds$eig
head(h.eig)

#plot the samples
p1 = ggplot(h.map, aes(Dim1, Dim2, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point() + theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=12), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1)) +coord_fixed(sqrt(h.eval[2] / h.eval[1])) + xlab("Dim 1 (21.2%)")+ ylab("Dim 2 (11.1%)") + ggtitle("a)")


#nmds on euclidean distance of chord transformation
c.euc = vegdist(otus.c, "euclidean")
c.nmds = cmdscale(c.euc, eig=TRUE, k=10)
c.map = data.frame(sample_data(index25), scores(c.nmds))
c.map$method = "Chord"
c.eig = 100*(c.nmds$eig/sum(c.nmds$eig))
c.eval = c.nmds$eig
head(c.eig)

#plot the samples
p2 = ggplot(c.map, aes(Dim1, Dim2, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point() + theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=12), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1)) +coord_fixed(sqrt(c.eval[2] / c.eval[1])) + xlab("Dim 1 (57.4%)")+ ylab("Dim 2 (20.4%)") + ggtitle("b)")


#nmds on vst-transformed species profiles
vst.euc = vegdist(otus.VST, "euclidean")
vst.nmds = cmdscale(vst.euc, eig=TRUE, k=10)
vst.map = data.frame(sample_data(index25), scores(vst.nmds))
vst.map$method = "VST"
vst.eig = 100*(vst.nmds$eig/sum(vst.nmds$eig))
vst.eval = vst.nmds$eig
head(vst.eig)

#plot the samples
p3 = ggplot(vst.map, aes(Dim1, Dim2, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point() + theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=12), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1)) +coord_fixed(sqrt(vst.eval[2] / vst.eval[1])) + xlab("Dim 1 (17.3%)")+ ylab("Dim 2 (10.4%)") + ggtitle("c)")


#nmds on bray curtis after vst-transforming species profiles
#replace values < 0 with 0
otus.VST[otus.VST < 1] <- 0
bray.euc = vegdist(otus.VST, "bray")
bray.nmds = cmdscale(bray.euc, eig=TRUE, k=10)
bray.map = data.frame(sample_data(index25), scores(bray.nmds))
bray.map$method = "vst_bray"
bray.eig = 100*(bray.nmds$eig/sum(bray.nmds$eig))
bray.eval = bray.nmds$eig
head(bray.eig)


#plot the samples
p4 = ggplot(bray.map, aes(Dim1, Dim2, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point() + theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=12), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1)) +coord_fixed(sqrt(vst.eval[2] / vst.eval[1])) + xlab("Dim 1 (25.3%)")+ ylab("Dim 2 (11.1%)") + ggtitle("d)")

RA.bray = vegdist(otus.ra, "euclidean")
RA.nmds = cmdscale(RA.bray, eig=TRUE, k=10)
RA.map = data.frame(sample_data(index25), scores(RA.nmds))
RA.map$method = "RA_Bray"
RA.eig = 100*(RA.nmds$eig/sum(RA.nmds$eig))
RA.eval = RA.nmds$eig
head(RA.eig)

#plot the samples
p5 = ggplot(RA.map, aes(Dim1, Dim2, color=Tooth_Class)) + facet_wrap(~Tooth_Aspect) + geom_point() + theme_bw() + guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=12), axis.text.x = element_text(angle=0, vjust=1))+theme(text = element_text(size=12), axis.text.x = element_text(angle=00, vjust=1)) +coord_fixed(sqrt(RA.eval[2] / RA.eval[1])) + xlab("Dim 1 (28.3%)")+ ylab("Dim 2 (21.9%)") + ggtitle("e)")


grid.arrange(p1, p2, p3, p4, p5, ncol=2)
#ggsave(grid.arrange(p1, p2, p3, p4, p5, ncol=2), file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS2.png",  width = 8.5, height = 11, units ="in",dpi = 300)

```


#plot the samples
df = data.frame(rbind(RA.map, h.map, c.map, vst.map, bray.map))
df$Tooth_Class = str_replace_all(df$Tooth_Class, "Incisor_Central", "Incisor")
buccal = subset(df, Tooth_Aspect=="Buccal")
lingual = subset(df, Tooth_Aspect=="Lingual")
p1=ggplot(buccal, aes(Dim1, Dim2, color=Tooth_Class)) + geom_point() + facet_wrap(~method, scales="free", ncol=5) + theme_bw() + ggtitle("a) Buccal") + guides(colour=guide_legend(title="Tooth Class"))
p2 = ggplot(lingual, aes(Dim1, Dim2, color=Tooth_Class)) + geom_point() + facet_wrap(~method, ncol=5,scales="free") + theme_bw() + ggtitle("b) Lingual") + guides(colour=guide_legend(title="Tooth Class")) 

#### Supplemental Figure 3: Separation of molars/incisors is robust to a variety of distance metrics 

```{r, fig.width=12, fig.height=6, warning=FALSE}
library(vegan)
###do relative abundance transformation and see if  the patterns are the same
indexRA  = transform_sample_counts(index25, function(x) x / sum(x) )
#replace the otu table with hellinger transformed data
otus = data.frame(otu_table(index25))
outs.h = decostand(otus, "hellinger")
otu_table(index25) = otu_table(outs.h, taxa_are_rows=FALSE)

#make a list of nmds objects
dist_methods_deco =  c("binomial", "bray", "canberra", "euclidean", "gower", "jaccard", "kulczynski", "manhattan")

nmds_ideco.list <- vector("list", length(dist_methods_deco))
plot_ideco.list <- vector("list", length(dist_methods_deco))     

for(i in 1:length(dist_methods_deco)){
        iDist <- vegan::vegdist(outs.h, method=dist_methods_deco[i])
        iMDS <- ordinate(index25, method="PCoA", distance=iDist, correction="lingoes")
        p <- plot_ordination(index25, iMDS, color="Tooth_Class") + facet_wrap(Jaw_Quadrant~Tooth_Aspect)
        ps <- p$data
        ps$Distance <- dist_methods_deco[[i]]
        plot_ideco.list[[i]] <- ps
        nmds_ideco.list[[i]] <- iMDS
}
plot_ideco <- do.call("rbind", plot_ideco.list) 
plot_ideco$Tooth_Class = str_replace_all(plot_ideco$Tooth_Class, "Incisor_Central", "Incisor")
p=ggplot(plot_ideco, aes(Axis.2, Axis.1, color=Tooth_Class)) + facet_wrap(Tooth_Aspect~Distance, ncol=8, scales="free") + geom_point() + theme_bw()+ guides(color=guide_legend(title="Tooth Class"))+ theme(text = element_text(size=10), axis.text.x = element_text(angle=00, vjust=1)) + xlab("Axis 2") + ylab("Axis 1")

#ggsave(p, file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS3.png",  width = 12, height = 8.5, units ="in",dpi = 300)

p
```

#### Separation of molars/incisors is also seen on the discovery dataset, sequenced to a different depth on a different platform

```{r, fig.width=12, fig.height=6, warning=FALSE}
library(vegan)
### apply a 10% filter
filtergroup = filterfun(kOverA(k=190, A=1)) #k = number of samples; A = abundance
        index = subset_samples(discovery, Class %in% c("CentralIncisor", "Molar"))
        index = filter_taxa(index, filtergroup, prune=TRUE) 
        index = prune_samples(sample_sums(index) > 0, index) 

        #note the following command drops 56 samples 
        index = prune_samples(sample_sums(index) > 200, index)

###do relative abundance transformation and see if  the patterns are the same
indexRA  = transform_sample_counts(index, function(x) x / sum(x) )

#make a list of nmds objects
dist_methods_deco =  c("binomial", "bray", "canberra", "euclidean", "gower", "jaccard", "kulczynski", "manhattan")


nmds_ideco.list <- vector("list", length(dist_methods_deco))
plot_ideco.list <- vector("list", length(dist_methods_deco))     
totus <- t(otu_table(indexRA))

for(i in 1:length(dist_methods_deco)){
        iDist <- vegan::vegdist(totus, method=dist_methods_deco[i])
        iMDS <- ordinate(indexRA, method="PCoA", distance=iDist, correction="lingoes")
        p <- plot_ordination(indexRA, iMDS, color="Class") + facet_wrap(Quadrant~Aspect)
        ps <- p$data
        ps$Distance <- dist_methods_deco[[i]]
        plot_ideco.list[[i]] <- ps
        nmds_ideco.list[[i]] <- iMDS
}
plot_ideco <- do.call("rbind", plot_ideco.list) 
p=ggplot(plot_ideco, aes(Axis.1, Axis.2, color=Class)) + facet_wrap(Aspect~Distance, ncol=8, scales="free") + geom_point() + theme_bw()+ guides(color=guide_legend(title="Tooth Class"))

p
```

###we also want to know whether the raw data showed differences in sequencing depth by tooth class
```{r, fig.height=8, fig.width=12}
df = data.frame(sample_sums(supra), sample_data(supra))
colnames(df)[1] = "sums"

df1 = subset(df, Tooth_Class %in% c("Molar", "Incisor_Central"))

#do incisors and molars differ by tooth class on buccal aspect
df1b = subset(df1, Tooth_Aspect=="Buccal")
wilcox.test(sums~Tooth_Class, data=df1b, exact=TRUE, conf.int=TRUE)

#what about lingual
df1b = subset(df1, Tooth_Aspect=="Lingual")
wilcox.test(sums~Tooth_Class, data=df1b, exact=TRUE, conf.int=TRUE)
```


### Supplementary Figure 4: Communities don't experience a directional change in composition over time
- Use multiple-tables approach where one table is defined for each day
```{r, fig.height=8, fig.width=12}
library(ade4)
#force the labeling of the subjects
ordering= c("Subject 1", "Subject 2",  "Subject 3" , "Subject 4" , "Subject 5" ,"Subject 6", "Subject 7" ,"Subject 8")
sample_data(index25)$Subject  <- factor(sample_data(index25)$Subject, levels = ordering)

#rename the index dataset
statis_vst <- Index25_VST

ProjHolder <-vector('list',length(subs)) 
CorrHolder <- vector('list', length(subs))

#set up a loop to do the statis for each individual separarelty
subs = levels(sample_data(statis_vst)$Subject)

for(i in 1:length(subs)){
  #subset on the subject
  subx = subset_samples(statis_vst, Subject==subs[[i]])
  subx = prune_samples(sample_sums(subx) > 0, subx)
  
  #do the statis and save projections into df
  m = matrix(otu_table(subx), ncol = nsamples(subx))
  m = t(m)
  dim(m)
  m = data.frame(m)
  kta1 = ktab.within(withinpca(m, sample_data(subx)$Day, scann = FALSE))
  statis1 = statis(kta1, scann = FALSE)
  statisProjs = statis1$C.Co[as.character(1:nsamples(subx)),]
  statisProjs = data.frame(sample_data(subx), statisProjs)
  ProjHolder[[i]] = statisProjs
  
  #look at the RV coefficient
  RVs <- data.frame(statis1$RV)
  RVs$rows <- rownames(RVs)
  rv.dfm <- melt(RVs, id.var="rows")
  colnames(rv.dfm) <- c("D1", "D2", "RV")
  d1 <- as.integer(str_replace_all(rv.dfm$D1, "X", ""))
  d2 <- as.integer(str_replace_all(rv.dfm$D2, "X", ""))
  interval <- abs(d1-d2)
  rv.dfm$interval <- interval
  rv.dfm <- subset(rv.dfm, interval !=0)
  rv.dfm$RV <- as.numeric(rv.dfm$RV)
  rv.dfm$Subject = subs[[i]]
  CorrHolder[[i]] = rv.dfm
  
}
rvdf <- data.frame(do.call("rbind", CorrHolder)) 
projDf <-data.frame(do.call("rbind", ProjHolder)) 

  
### Plot the RV coefficients
library(ggpmisc)
my.formula<- y ~ x
p1=ggplot(rvdf, aes(interval, RV)) + facet_wrap(~Subject, ncol=4) + theme_bw() + xlab("Time Interval between Sample Collection Days")  + stat_poly_eq(formula = my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE)  + geom_point() + ylim(0, 1)+ geom_smooth(method="lm") + ylab("RV Coefficient")


#plot points
ordering= 1:32
projDf$Day  <- factor(projDf$Day, levels = ordering)

p2 <- ggplot(projDf, aes(as.numeric(Day), C1, color = Tooth_Class)) +  geom_smooth(method="glm") + geom_point()+facet_wrap(~ Habitat) + theme_bw() + ggtitle("C1 Scores by Site Over Time") + xlab("Day") + stat_poly_eq(formula = my.formula, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) 


plot(p1)
plot(p2)



#save supplementary figure S4
#ggsave(p1, file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS4.png",  width = 7, height = 7, units ="in",dpi = 300, device="png")   
```

### Supplemental Figure 5: Lesser abundant taxa drive the gradient
- the gradient becomes increasingly apparent as additional taxa are added

```{r, fig.height=8, fig.width=12}
#generate multiple plots based on the top most abundant taxa
library(ggcorrplot)

thresh = c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
holder <-vector('list',length(thresh)) 

otus = data.frame(otu_table(FullMouth))
otus.h = decostand(otus, "hellinger")
otu_table(FullMouth) = otu_table(otus.h, taxa_are_rows=FALSE)

for(i in 1:length(thresh)){ 

  sub = names(sort(taxa_sums(FullMouth), TRUE)[1:thresh[i]]) 
  sub1   <- prune_taxa(sub, FullMouth)
  
  map <- sample_data(FullMouth)
  coo <- cbind(map$x, map$y)
  colnames(coo) <- c("x", "y")

  ### Perform  PCA-IV with respect to a 3rd order polynomial of geographic coordinates
  poly.xy3 <- poly(coo, degree = 3, raw=FALSE) #, coefs=TRUE) 
  colnames(poly.xy3) <- c("X", "X^2", "X^3", "Y", "XY", "X^2Y", "Y^2", "XY^2", "Y^3")
  poly.xy3.df <- data.frame(poly.xy3, map$x, map$y)

  library(ade4)
  totus <- data.frame(otu_table(sub1))
  rld.pca <- dudi.pca(totus, center=TRUE, scale=TRUE, scannf=FALSE, nf=10)
  rld.xy3 <- pcaiv(rld.pca, poly.xy3, scannf = FALSE, nf = 6)
  rld.xy3.df <- data.frame(rld.xy3$ls, map)
  xy3.df <- data.frame(rld.xy3.df, poly.xy3)
  
  # how much of the variance does this model explain?
  rld.xy3.var <- sum(rld.xy3$eig)/sum(rld.pca$eig)*100
  rld.xy3.var
  
  # get the eigen values
  pca.scree <- data.frame(rank = 1:length(rld.xy3$eig))
  Explainedvariance = rld.xy3$eig/sum(rld.xy3$eig)*100
  Explainedvariance

  #force x, y to numeric
  xy3.df$x <- as.numeric(as.character(xy3.df$x))
  xy3.df$y <- as.numeric(as.character(xy3.df$y))
  
  #add the treshold
  xy3.df$Threshold = thresh[i]
  
  holder[[i]] = xy3.df
  
}

df <- data.frame(do.call("rbind", holder)) 
ordering= 1:32
df$Tooth_Number  <- factor(df$Tooth_Number, levels = ordering)
df$Tooth_Class = str_replace_all(df$Tooth_Class, "Incisor_Central", "Central Incisor")
df$Tooth_Class = str_replace_all(df$Tooth_Class, "Incisor_Lateral", "Lateral Incisor")
df$Tooth_Class = str_replace_all(df$Tooth_Class, "Molar_Pre", "Pre-molar")
p=ggplot(df, aes(Tooth_Number, Axis1, fill=Tooth_Class)) + geom_boxplot() + facet_wrap(~Threshold, ncol=5) + theme_bw()+ scale_x_discrete(breaks = seq(from=0, to=30, by=5), labels=seq(from=0, to=30, by=5)) + xlab("Tooth Number")+ theme_bw() + guides(fill=guide_legend(title="Tooth Class")) + ylab("Axis 1")
p
#ggsave(p, file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS5.png",  width = 11, height = 8.5, units ="in",dpi = 300, device = "png")  
```

##### Supplemental Figure 6 - Moran's coefficients on taxa distributions

```{r, fig.width=10, fig.height=8, warning=FALSE}
library(spdep);library(plyr)
#take the mean value of each taxon at each site; in effect, average across sub1jects
hab <- merge_samples(sub2, group="Habitat")
sample_data(hab)$Habitat <- factor(sample_names(hab))

#make a new mapping file for plotting
foo <- data.frame(sample_names(hab))
colnames(foo)[1] = "Habitat"
map = read.csv("~/Desktop/Proctor_NatureComm/mytoothdot_coordinates_FullMouth.csv")
colnames(map)[1] = "Habitat"
map = join(foo, map, by="Habitat")
rownames(map) = map$Habitat
sample_data(hab)=map
coo = data.frame(map$x, map$y)

#Compute the Inverse Euclidean Distance between samples
EucMat <- as.matrix(dist(coo, method="euclidean", diag=TRUE, upper=FALSE))
EucInv <- 1/EucMat
diag(EucInv) <- 0
#convert the square matrix into a listw object using mat2listw
Euc.invw <- mat2listw(EucInv, row.names=NULL, style="M")
# set the seed
set.seed(1234)
# compute Moran.I using the Euclidean Distance Metric
smotus <- data.frame(otu_table(hab))
Euc.mct <- sapply(smotus, moran.test, Euc.invw, randomisation=TRUE, 
                  alternative="greater", rank=TRUE, na.action=na.omit, simplify=FALSE, USE.NAMES=TRUE)

# unlist the Moran.I test and combine with the taxonomy table
Euc.mct1 <- data.frame(matrix(unlist(Euc.mct), nrow=ntaxa(hab), byrow=T), tax_table(hab))
colnames(Euc.mct1)[1:6] <- c("Moran.I.SD", "p.value", "Moran.I", "Expectation", "Variance","Alternative")

### For the values to numeric so they can later be plotted
Euc.mct1$p.value <- as.numeric(levels(Euc.mct1$p.value))[Euc.mct1$p.value]
Euc.mct1$Moran.I <- as.numeric(levels(Euc.mct1$Moran.I))[Euc.mct1$Moran.I]

### Construct confidence intervals around Moran's I
Euc.mct1$lower = Euc.mct1$Moran.I - as.numeric(Euc.mct1$Moran.I.SD)
Euc.mct1$upper = Euc.mct1$Moran.I + as.numeric(Euc.mct1$Moran.I.SD)

##plot moran's I as a function of p-value
Euc.mct1$Sig = ifelse(Euc.mct1$p.value < 0.05, "Significant", "Not Significant")
p1= ggplot(Euc.mct1, aes(Highest.Rank, Moran.I, color=Sig)) + geom_point() + theme_bw()+ theme(text = element_text(size=12), axis.text.x = element_text(angle=90, vjust=1)) + xlab("Taxon") + scale_color_discrete(name="Significance\nLevel") + ylab("Moran's I (Correlation Coefficient)")
p1

#save figure S6
#ggsave(p1, file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS6.png",  width = 10, height = 8, units ="in",dpi = 300, device = "png")
```

### Supplemental Figure 7: Other axes; significant polynomial terms
- this is in the quickPCNM script

### Supplemental Figure 8: PCNM
- this is in the quickPCNM script

### Supplemental Figure 9: MEM
- this is in the quickPCNM script

### Supplemental Figure 10: shedding and non-shedding surfaces are distinct habitats

```{r, fig.height=8, fig.width=12}
#convert to RA for pcoa
otus= data.frame(otu_table(Biogeo2_phys15))
otus.h = decostand(otus, "hellinger")
h.euc = vegdist(otus.h, "euclidean")

#make supplementary figure s6
h.nmds = cmdscale(h.euc, eig=TRUE, k=10)
h.map = data.frame(sample_data(Biogeo2_phys15), scores(h.nmds))
h.eig = 100*(h.nmds$eig/sum(h.nmds$eig))
head(h.eig)

evals <- h.nmds$eig
h.map$Subject = str_replace_all(h.map$Subject, "(4-101)", "Subject 1")
h.map$Subject = str_replace_all(h.map$Subject, "(4-102)", "Subject 2")
h.map$Subject = str_replace_all(h.map$Subject, "(4-103)", "Subject 3")

#Make supplemental figure 9
FigS9a = ggplot(h.map, aes(Dim1, Dim2, color=TissueClass)) + facet_wrap(~Subject) + theme_bw() + geom_point(alpha=0.8) + guides(color=guide_legend(title="Tissue type"))+coord_fixed(sqrt(evals[2] / evals[1])) + xlab("Axis 1 (35.9%)") + ylab("Axis 2 (16.9%)") + ggtitle("a) Tissue type")

FigS9b = ggplot(h.map, aes(Dim1, Dim2, color=Site.New)) + facet_wrap(~Subject) + theme_bw() + geom_point(alpha=0.8) + guides(color=guide_legend(title="Body site habitat") )+coord_fixed(sqrt(evals[2] / evals[1]))+ xlab("Axis 1 (35.9%)") + ylab("Axis 2 (16.9%)") + ggtitle("b) Body site habitat")
grid.arrange(FigS9a, FigS9b, ncol=1)
FigS9 = arrangeGrob(FigS9a, FigS9b, ncol=1)

#ggsave(FigS9, file="~/Dropbox/Figures_20170617/Revised/FinalFigures/Figure10.png",  width = 7, height = 7, units ="in",dpi = 300, device="png")     
```

#### Supplemental figure 10; Forward selection mucosal biogeography
- this is in the main script


#### Supplemental figure 12; what is the distribution of caries in each mouth
#### 5.2. Bring in the clinical data - in this section, we bring in caries 
- note that we examined the occlusal surfaces as well, but those data are not represented here since we only sampled the buccal and lingual surfaces of teeth
- We see that in general the caries experience of SS subjects is widespread whereas for the control subjects it's limited to the molars and incisors
- Important to note that these data only represent the smooth surfaces!!

```{r, fig.width=12, fig.height=6, warning=FALSE}
library(doBy)
#read in the caries data and then subset on the redcap ids that are included in the dataset
data = read.csv("~/Desktop/Proctor_NatureComm/data_caries_combined_v1.2_20170328.csv")
colnames(data)[3] = "redcap_record_num"
data1 = subset(data, redcap_record_num %in% redcap.id)

#subset on buccal and lingual (excluding the occlusal surfaces as well as the mesial- and distal- sites) and get rid of wisdom teeth
bl = subset(data1, surface %in% c("B", "L"))
nowise = c(2:15, 18:31)
bl = subset(bl, tooth %in% nowise)

#convert disease to 1, sound to 0
bl$binary = ifelse(bl$description =="SOUND", 0, 1)

#count the number of decayed missing teeth per subject
bl.sum = summaryBy(binary~redcap_record_num, data=bl, FUN=sum)
bl.sum$prop = bl.sum/28
colnames(bl)[3]= "redcap_record_num"
colnames(bl)[8]= "Tooth_Number"
colnames(bl)[9]= "Tooth_Aspect"
bl$Tooth_Aspect = str_replace_all(bl$Tooth_Aspect, "([B,L])", replacement =c("Buccal", "Lingual"))
bl = bl[,3:11]


#join the caries data with the microbial data
total3 = join(flow.map2, bl, b=c("redcap_record_num", "Tooth_Number", "Tooth_Aspect"))
total3$x <- as.numeric(as.character(total3$x))
total3$y <- as.numeric(as.character(total3$y))
rownames(total3) = total3[,1]
total3 = sample_data(total3)

# relabel the subjects so they will correspond to the way they are labeled in figure 5
#relabel controls that have symetrical gradients
total3$Subject = str_replace_all(total3$Subject, "1-101", "Control 01")
total3$Subject = str_replace_all(total3$Subject, "1-103", "Control 02") 
total3$Subject = str_replace_all(total3$Subject, "1-104", "Control 03") 
total3$Subject = str_replace_all(total3$Subject, "1-106", "Control 04") 
total3$Subject = str_replace_all(total3$Subject, "1-107", "Control 05") 

#relabel the controls that have flat maxillary lines
total3$Subject = str_replace_all(total3$Subject, "1-102", "Control 06")
total3$Subject = str_replace_all(total3$Subject, "1-105", "Control 07") 


#relabels sjogrens that have symetrical curves
total3$Subject = str_replace_all(total3$Subject, "3-305", "Sjogrens 01") 
total3$Subject = str_replace_all(total3$Subject, "3-302", "Sjogrens 02") 
total3$Subject = str_replace_all(total3$Subject, "3-306", "Sjogrens 03") 


#relabel sjogren's that have flat lines
total3$Subject = str_replace_all(total3$Subject, "3-304", "Sjogrens 04") 
total3$Subject = str_replace_all(total3$Subject, "3-308", "Sjogrens 05") 
total3$Subject = str_replace_all(total3$Subject, "3-310", "Sjogrens 06") 
total3$Subject = str_replace_all(total3$Subject, "3-309", "Sjogrens 07") 


total3$Subject = str_replace_all(total3$Subject, "3-303", "Sjogrens 08") 
total3$Subject = str_replace_all(total3$Subject, "3-307", "Sjogrens 09") 

#relabel sjogrens that have exaggerated  lines

total3$Subject = str_replace_all(total3$Subject, "3-301", "Sjogrens 10") 
total3$Tooth_Class = str_replace_all(total3$Tooth_Class, "Incisor_Central", "Central Incisor")
total3$Tooth_Class = str_replace_all(total3$Tooth_Class, "Incisor_Lateral", "Lateral Incisor")
total3$Tooth_Class = str_replace_all(total3$Tooth_Class, "Molar_Pre", "Pre-molar")

p=ggplot(total3, aes(x, y, size=as.factor(binary), color=Tooth_Class)) + geom_point() + facet_wrap(~Subject, ncol=5) + theme_bw()+ guides(colour=guide_legend(title="Tooth Class"))
p
ggsave(p, file="~/Dropbox/FigureS12.eps",  width = 10, height = 8.5, units ="in",dpi = 300, device="eps") 


#why does aim 1 have any of the smooth surface caries? are these actually restorations, or are they fluoride treatments?
sa1 = subset(total3, Aim=="SA1")

p=ggplot(sa1, aes(x, y, size=binary, color=Tooth_Class)) + geom_point() + facet_wrap(~Subject) + theme_bw() 
p # we see that this is in two subject, 1104 and 1105
#take a look at those sites in those subjects
s1 = subset(sa1, Subject %in% c("Control 03", "Control 07"))

p=ggplot(s1, aes(x, y, size=binary, color=Tooth_Class, label=description)) + geom_point() + facet_wrap(~Subject) + theme_bw() + geom_text()
p # we see that this is in two subject, 1104 and 1105 and that these subjects have amalgams and composites on these sites
```

#### Supplemental figure  13: what taxa segregate across CCA axis 1 scores

```{r, fig.height=8, fig.width=12}
#how many samples and subjects are there?
flow 
levels(sample_data(flow)$Subject) #7 controls; 10 aim 3

#get ridof subjects with missing flow rate for the cca
flows = subset_samples(flow, UWS_FR & SWS_FR != "NA")
levels(sample_data(flows)$Subject) #7 controls; lost subject 3-310 because of sws-fr


#subset on taxa present in 10% of samples
filtergroup = filterfun(kOverA(k=75, A=1)) #k = number of samples; A = abundance
        flows = filter_taxa(flows, filtergroup, prune=TRUE) 
        flows = prune_taxa(taxa_sums(flows) > 0, flows)
        flows = prune_samples(sample_sums(flows) > 0, flows)
        flows
        
#stabilize the variance
flows_VST = flows
otu_table(flows_VST) <- otu_table(flows_VST) + 1
flows.ds = phyloseq_to_deseq2(flows_VST, ~PoolName)

#variance stabilizing transformation
flows_vst <- varianceStabilizingTransformation(flows.ds , blind=FALSE, fitType="local") 
counts_VST <- otu_table(as.matrix(assay(flows_vst)), taxa_are_rows=TRUE)
otu_table(flows_VST) <- counts_VST 

#set an analysis up for CCA
otus = t(otu_table(flows_VST))
map1 = data.frame(sample_data(flows_VST)$Tooth_Class, sample_data(flows_VST)$UWS_FR, sample_data(flows_VST)$SWS_FR, sample_data(flows_VST)$binary)
colnames(map1) = c("Class", "uws_fr", "sws_fr", "dmfs")
map1$Class = as.numeric(map1$Class)
subs = as.vector(sample_data(flows_VST)$Subject)
runs = as.vector(sample_data(flows_VST)$Pool_Name)

#for some reason this wworks on the command line but not in knitr
attach(map1)
flow.cca = vegan::cca(otus ~ map1$Class*map1$uws_fr*map1$sws_fr*map1$dmfs, sitenv=map1)

#run an anova on this
set.seed(100)
flow.aov = anova.cca(flow.cca, by="term", strata=subs)
flow.aov


## get the species scores and plot them
sp.cca = data.frame(as.matrix(flow.cca$CCA$v))

species = data.frame(taxa_sums(flows_VST), sp.cca, tax_table(flows_VST), otu_table(flows_VST))
colnames(species)[1] = "sums"
species$tax = paste0(species$Genus, "_", species$Species)
species$tax = str_replace_all(species$tax, "_NA", " sp.")
species$seq = rownames(species)
sp.df = melt(species, id.var=c("tax", "sums", "seq", colnames(tax_table(flows_VST)), colnames(sp.cca))) 

#subset on taxa with high or low scores along CCA1
df2 = subset(sp.df, CCA1 < -1 | CCA1 > 1)
df2 = subset(df2, Genus !="NA")


p7 = ggplot(df2, aes(Genus, CCA1, color=Genus, label=Highest.Rank)) + geom_text(size=3, angle=45)  + theme_bw() +theme(legend.position = "none")+ theme(text = element_text(size=12), axis.text.x = element_text(angle=90, vjust=1))+ ylab("CCA1 (59.74%)")

#ggsave(p7, file="~/Dropbox/Figures_20170617/Revised/FinalFigures/FigureS13.png",  width = 11, height = 8.5, units ="in",dpi = 300, device="png")
p7
```
 
 
### Save the workspace
```{r}
save.image(file="Proctor_SuppFigures_v20.0.Rdata")
```
